Efficient inference using the approximate Riemannian geometry of stochastic population models

### 2012-08-02 paper/paper.tex
Added section headings

Inference for MJP is difficult: non-linear likelihood, computational
  expensive, proposals expensive, analytically intractable likelihood
\item Data: Partially observed discrete, noisy time-course.
\item Existing work for likelihood evaluations: 
\begin{itemize}
\item Likelihood calculations
\begin{itemize}
\item Exact: Boys et al, slow, not noise
\item Approx SDE - Andy and Darren (with Noise)
\item Approx MC - Andy and Colin (no noise)
\item Approx LNA - Mark (no noise), Kolmo' (no noise, but check)
\end{itemize}
\item New:
\begin{itemize}
\item Approximate proposal mechanism based on the geometry of MC
\begin{itemize}
\item Overcome strong correlation structure which is standard with partially
  observed data
\item Fast proposals based on approximate geometry
\item Accept/reject with approximate model before trying exact model
\end{itemize}
\item Inference is exact
\item Including observational error
\item Time course measurements, unlike Mark's LNA
\end{itemize}
\item Examples:
\begin{itemize}
\item Immigration-death model: exact proposal compared with approximate proposal
  (no noise)
\item Aphid model: 3 blocks * 3 water treats * 3 nitro treats with Poisson error
\item Hidden states (counts), updated using standard method
\end{itemize}
\end{itemize}
\end{itemize}
\end{abstract}

@@

@@

\subsection{Approximate Riemannian Geometry}

@@

Key point: little overhead for approximate likelihood

@@

\begin{itemize}
\item Comparison between approximate proposal and true proposal
\item Comparison between LNA and MC?
\item Three examples: increase correlation
\end{itemize}

\subsection{Independent time course}

Bimodal example??

\subsection{Aphid simulation study}

\section{Aphid real}

>>>>

Inference for MJP is difficult: non-linear likelihood, computational
  expensive, proposals expensive, analytically intractable likelihood
\item Data: Partially observed discrete, noisy time-course.
\item Existing work for likelihood evaluations: 
\begin{itemize}
\item Likelihood calculations
\begin{itemize}
\item Exact: Boys et al, slow, not noise
\item Approx SDE - Andy and Darren (with Noise)
\item Approx MC - Andy and Colin (no noise)
\item Approx LNA - Mark (no noise), Kolmo' (no noise, but check)
\end{itemize}
\item New:
\begin{itemize}
\item Approximate proposal mechanism based on the geometry of MC
\begin{itemize}
\item Overcome strong correlation structure which is standard with partially
  observed data
\item Fast proposals based on approximate geometry
\item Accept/reject with approximate model before trying exact model
\end{itemize}
\item Inference is exact
\item Including observational error
\item Time course measurements, unlike Mark's LNA
\end{itemize}
\end{itemize}
\end{itemize}
\end{abstract}

@@

C \& B

@@

CSG

\subsection{Approximate Riemannian Geometry}
BC

@@

?
Key point: little overhead for approximate likelihood

@@

\begin{itemize}
\item Comparison between Riemannian MC proposal, LNA proposal and true proposal
\item Comparison between Riemannian and MH
\item A single example, with highly correlated parameters
\end{itemize}

\subsection{SIR (type) model}

\begin{itemize}
\item Use model from Stumpf ABC paper (with real data?)
\end{itemize}

\subsection{Aphid data set}

\begin{itemize}
\item 36 parameters - 18 birth, 18 death. 3 water treatments, 3 nitrogen treatments and 3 blocks, with interactions
\item 5*27 (I think) latent data sets
\item Exploit Sub-mannifolds for choosing parameter sets
\item Poisson error structure
\end{itemize}
